Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-06-21 paper/paperv3.qmd
more dashed line updates

duration_plot <- ggpredict(
  pheno_model, 
  terms = c("age10 [all]", "phase", "year [all]")
) %>% 
  as_tibble() %>% 
  transmute(age = x * 10,
            dur_days = predicted,
            dur_days_lwr = conf.low,
            dur_days_upr = conf.high,
            phase = group,
            year = as.numeric(as.character(facet))) %>% 
  left_join(n_phenology, by = "year") %>% 
  group_by(age, phase) %>% 
  summarize(across(starts_with("dur_days"), \(x) weighted.mean(x, n)),
            .groups = "drop") %>% 
  ggplot(aes(age)) +
  geom_ribbon(aes(ymin = dur_days_lwr, ymax = dur_days_upr, fill = phase),
              alpha = 0.25) +
  geom_pointrange(aes(y = dur_days, 
                      ymin = dur_days_lwr, 
                      ymax = dur_days_upr,
                      color = phase),
                  pheno_raw,
                  position = position_dodge(width = 0.5)) +
  geom_line(aes(y = dur_days, color = phase)) +
  annotate("text", 12, 14, label = "Molting", color = "#E09A2D", hjust = 0) +
  annotate("text", 12, 32, label = "Breeding", color = "#D05794", hjust = 0) +
  scale_fill_manual(values = c("#D05794", "#E09A2D")) +
  scale_color_manual(values = c("#D05794", "#E09A2D")) +
  labs(x = "Maternal age (years)",
       y = "Phase duration (days)") +
  theme(legend.position = "none")

>>>>

duration_plot <- ggpredict(
  pheno_model, 
  terms = c("age10 [all]", "phase", "year [all]")
) %>% 
  as_tibble() %>% 
  transmute(age = x * 10,
            dur_days = predicted,
            dur_days_lwr = conf.low,
            dur_days_upr = conf.high,
            phase = group,
            year = as.numeric(as.character(facet))) %>% 
  left_join(n_phenology, by = "year") %>% 
  group_by(age, phase) %>% 
  summarize(across(starts_with("dur_days"), \(x) weighted.mean(x, n)),
            .groups = "drop") %>% 
  ggplot(aes(age)) +
  geom_ribbon(aes(ymin = dur_days_lwr, ymax = dur_days_upr, fill = phase),
              alpha = 0.25) +
  geom_pointrange(aes(y = dur_days, 
                      ymin = dur_days_lwr, 
                      ymax = dur_days_upr,
                      color = phase),
                  pheno_raw,
                  position = position_dodge(width = 0.5)) +
  geom_line(aes(y = dur_days, color = phase, linetype = phase)) +
  annotate("text", 12, 14, label = "Molting", color = "#E09A2D", hjust = 0) +
  annotate("text", 12, 32, label = "Breeding", color = "#D05794", hjust = 0) +
  scale_fill_manual(values = c("#D05794", "#E09A2D")) +
  scale_color_manual(values = c("#D05794", "#E09A2D")) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  labs(x = "Maternal age (years)",
       y = "Phase duration (days)") +
  theme(legend.position = "none")
